Creation of prediction maps

### 2019-05-03 analysis/rmd/defoliation-maps.Rmd
defoliation-maps: VI derivations working

```{r setup}
knitr::opts_knit$set(base.dir = 'analysis/rmd/')
knitr::opts_chunk$set(fig.retina=3, fig.align = 'center',
                      out.width = "100%")
loadd(defoliation_raster_2017, defoliation_raster_2018,
      defoliation_df_2017, defoliation_df_2018)
```

>>>>

```{r setup}
knitr::opts_knit$set(base.dir = 'analysis/rmd/')
knitr::opts_chunk$set(fig.retina=3, fig.align = 'center',
                      out.width = "100%")
loadd(defoliation_raster_2017, defoliation_raster_2018,
      defoliation_df)
```
